Untitled

### 2023-08-21 code/analysis_Redo.Rmd
adding payor to TE*Dist estimates

         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total,Qcomp, Altman, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)

@@

for (j in 10:12){

  df.temp <- df.core[,c(1:9, j, 13:ncol(df.core))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year, 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

@@

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total:Altman) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total:Altman) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

@@

#splits <- quantile(dfc[dfc$Year == 2011,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_expense, c(0.5), na.rm = TRUE)
splits <- quantile(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, c(0.5), na.rm = TRUE)

@@

@@

@@

#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.5), na.rm = TRUE)

@@

df.spill2 <- df.spill2 %>% 
  ungroup() %>% 
  #filter(MarketShare < median(MarketShare, na.rm = TRUE)) %>% 
  select(`BHCMIS ID`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients) %>%
  #inner_join(df.qual.exp %>% filter(Year == 2012) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`BHCMIS ID`, ZipFilter), by = c("BHCMIS ID")) %>% 
    select(Tx, D, Dist, Year, Zip, `BHCMIS ID`, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients) # %>% filter(ZipFilter == 2)

  i <- 10
  df.temp <- df.spill2[,c(1:5, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]

for (i in 11:15){
  df.temp <- df.spill2[,c(1:5, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", 'Outcome')
  model_feols_clustered <- feols(Outcome ~ Tx*as.numeric(Dist / 10) + D | Year + Zip, cluster = ~ Zip, data = df.temp)
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
}

p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), NumberofPatients = mean(NumberofPatients, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, Total.Hours)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), NumberofPatients = mean(NumberofPatients, na.rm = TRUE), Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, Total.Hours, Total.Hours)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = NumberofPatients - NumberofPatients.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 250) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Figure 4 - Unadjusted DID Estimates by Distance to Competitive Zip")

@@

output <- cbind(TEs %>% 
  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
    select(Estimate,`95% LB`, `95% UB`) ,

TEs_Dist %>% 
  mutate(`95% LB` = Estimate - `Std..Error` * 1.96, 
         `95% UB` = Estimate + `Std..Error` * 1.96) %>% 
    select(Estimate,`95% LB`, `95% UB`)) 
rownames(output) <- c("Hours Per Week","Locations","Perminance","Weekly Schedule","Calendar Schedule","Total")

round(output[c(6, 2,3, 1, 4, 5),], digits = 3) %>% 
  kable("html", booktabs = T, col.names = c("DID Estimate", "95% LB", "95% UB", "DID Estimate", "95% LB", "95% UB")) %>%
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Patient Panel" = 1, "Extensive Margin" = 2, "Intensive Margin" = 3)) %>% 
  add_header_above(c(" " = 1, "Treatment Effect" = 3, "Treatment Effect * Distance" = 3)) %>% 
  add_footnote(c("Treatment Effect is the ATT estimated in the zip code where the rival opens their new location","Treatment Effect * Distance is the change in the ATT for every 10km an outlying zip code in the incumbent's service area is from the competitive zip "))

@@

## NumberofPatients and Total.Hours are the best cases, controlling for Sites
```{r}

 i <- 10
  df.temp <- df.spill2[,c(1:5, 11, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]

for (i in 12:15){
  df.temp <- df.spill2[,c(1:5, 11, i)]
  names(df.temp) <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10))  ,
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),])
}

  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total"),   TEs, TEs_Dist)
```

>>>>

         crc.rate = crc.rate * 100, 
         pap.rate = pap.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         htn.rate = htn.rate * 100, 
         dm.rate = dm.rate * 100) %>% 
  select(`BHCMIS ID`, value, Tx, Year, Att, Att.random, year.rel, ID, STATE, 
         Total,Qcomp, Altman, Sites, #MCD:COM, 
         #crc.rate, pap.rate, childbmi.rate, adultbmi.rate, htn.rate, dm.rate, 
         #Liquidity:NetWorth, 
         Pct.NHA:Pct.COM) #%>%  mutate(Altman = ifelse(is.infinite(Altman), NA, Altman))#, #pap.rate:dm.total, Liquidity:Altman)

@@

for (j in 10:13){

  df.temp <- df.core[,c(1:9, j, 13:ncol(df.core))]
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp , 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHB + Pct.HL + Pct.LessThan100pctFPL | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )
  did.core <- rbind(did.core, outcomes$coeftable)
}

@@

df.core %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total:Sites) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total:Sites) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(did.core) %>% 
   select(name, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted, Estimate, `Std. Error`) %>% 
  mutate(Estimate = round(Estimate, 2), 
         `95% CI` = paste(round(Estimate - 1.96 * `Std. Error`, 2), ", ", round(Estimate + 1.96 * `Std. Error`, 2), sep = ""), 
         `% Change` = round(Estimate / `1_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 3))

@@

#splits <- quantile(dfc[dfc$Year == 2011,]$ngla_net_gain_loss / dfc[dfc$Year == 2010,]$ngla_expense, c(0.5), na.rm = TRUE)
splits <- quantile(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, c(0.25, 0.5, 0.75), na.rm = TRUE)

splits <- c(mean(dfc[dfc$year.rel == -1,]$ngla_net_gain_loss / dfc[dfc$year.rel == -1,]$ngla_expense, na.rm = TRUE))

@@

splits <- mean.nas(dfc[dfc$year.rel == -1,]$Total)

@@

## Effects startified by liquidity
```{r}

#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
splits <- quantile(dfc[dfc$year.rel == -1,]$quick_ratio, c(0.5), na.rm = TRUE)

splits <- mean.nas(dfc[dfc$year.rel == -1,]$quick_ratio)

df.liquid <- dfc %>% 
  mutate(MCD = Total * Pct.MCD / 100, 
         None = Total * Pct.None / 100, 
         MCR = Total * Pct.MCR / 100, 
         COM = Total * Pct.COM / 100,

df.liquid <- df.liquid %>% 
  left_join(dfc %>% filter(Year == 2010) %>% select(ID, quick_ratio) %>% 
  mutate(liquid = quick_ratio) , by = c("ID")) # %>% filter(`BHCMIS ID` %notin% c("010450","070430"))

splits1 <- c(min(df.liquid$liquid, na.rm = TRUE)-1, splits)
splits2 <- c(splits, max(df.liquid$liquid, na.rm = TRUE))

did.liquid <- c(0, 0, 0, 0)
for (g in 1:(length(splits) + 1)){
  for (j in 10:12){

  df.temp <- df.liquid[,c(1:9, j, 13:ncol(df.liquid))] 
  colnames(df.temp)[10] <- "Outcome"
  outcomes <- did2s(
      data = df.temp %>% filter(liquid > splits1[g] & liquid <= splits2[g]), 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage = ~ i(Tx, ref = FALSE),
        cluster_var = "ID",
      verbose = FALSE
    )

  did.liquid <- rbind(did.liquid, outcomes$coeftable)

did.liquid <- did.liquid[-1,]
rownames(did.liquid) <- NULL

data.frame(Subset = sort(rep(1:(length(splits) + 1), 3)),
      Outcome = rep(c("Total","Quality","Financial"), (length(splits) + 1)),
      Estimate = as.numeric(did.liquid[,1]), 
      SD = as.numeric(did.liquid[,2])) %>% 
  mutate(Subset.f = as.factor(Subset)) %>% 
  ggplot(aes(y = Subset.f, x = Estimate, xmin = Estimate - SD * 1.95, xmax = Estimate + SD * 1.95)) + 
  geom_point() + 
  xlab("Staggered 2-way DID Estimates") + 
ylab(NULL) + 
#adds the CIs
geom_errorbarh(height=.1) +

#sets the scales
#note that I reverse the y axis to correctly order the effect #liquids based on my index variable
#scale_x_continuous(limits=c(-2.5,1), breaks = c(-2.5:1), name=xname)+
#scale_y_continuous(name = "", breaks=1:9, labels = t9.forest$X1, trans="reverse")+

#faceting based on my subgroups
  #facet_wrap(~X1) +
facet_grid(~Outcome, scales= "free_x", switch = 'y', space = "free_y") +  
      theme_tufte_revised()+
   theme(strip.placement = "outside") +
#theme(text=element_text(family="Times",liquid=12, color="black"))+
theme(panel.spacing = unit(1, "lines")) + 
  ggtitle("DID Estimates by Baseline Liquidity")

@@

#splits <- quantile(dfc[dfc$Year == 2011,]$Total, c(0.5), na.rm = TRUE)
splits <- quantile(df.dist[df.dist$year.rel == -1,]$Dist.random, c(0.33, 0.66), na.rm = TRUE)

@@

df.spill2 <- df.spill2 %>% 
  ungroup() %>% 
  #filter(MarketShare < median(MarketShare, na.rm = TRUE)) %>% 
  select(`BHCMIS ID`, Tx, D, Att, Att.viz, Dist, Dist.rounded, Year, Zip, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients:Private) %>%
  #inner_join(df.qual.exp %>% filter(Year == 2012) %>% mutate(ZipFilter = ifelse(`Surplus as a pct of before dep expenses` < 2, 1, 2)) %>% select(`BHCMIS ID`, ZipFilter), by = c("BHCMIS ID")) %>% 
    select(Tx, D, Dist, Year, Zip, `BHCMIS ID`, Att, Att.viz, Dist.rounded, Total.Hours, Sites, Perminance, Schedule, Calendar, NumberofPatients:Private) # %>% filter(ZipFilter == 2)

p.spill <- df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >=  Att.viz, 1, Tx)) %>% 
  filter(Att > 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE)) %>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites = Sites_1 - Sites_0, 
         NumberofPatients = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours = Total.Hours_1 - Total.Hours_0) %>% 
  left_join(df.spill2 %>% 
  mutate(Treats = ifelse(Att == 0 & Year >= Att.viz, 1, Tx)) %>% 
  filter(Att == 0) %>% 
  group_by(Dist.rounded, Treats) %>% 
  summarise(Counts = n(), Sites = mean(Sites, na.rm = TRUE), 
            NumberofPatients = mean(NumberofPatients, na.rm = TRUE), 
            NumberofPatients_Medicaid = mean(Medicaid, na.rm = TRUE), 
            Total.Hours = mean(Total.Hours, na.rm = TRUE))%>% 
  pivot_wider(id_cols = Dist.rounded, names_from = Treats, values_from = c(Counts, Sites, NumberofPatients, NumberofPatients_Medicaid, Total.Hours)) %>% 
  mutate(Sites.control = Sites_1 - Sites_0, 
         NumberofPatients.control = NumberofPatients_1 - NumberofPatients_0, 
         NumberofPatients_Medicaid.control = NumberofPatients_Medicaid_1 - NumberofPatients_Medicaid_0, 
         Total.Hours.control = Total.Hours_1 - Total.Hours_0) %>% 
    select(Dist.rounded, Sites.control:Total.Hours.control), by = c("Dist.rounded")) %>% 
  mutate( Locations = Sites - Sites.control, 
         `Patients` = NumberofPatients - NumberofPatients.control, 
         `Patients - Medicaid` = NumberofPatients_Medicaid - NumberofPatients_Medicaid.control, 
         `Hours per Week` = Total.Hours - Total.Hours.control) %>% 
  select(Dist.rounded:Counts_1, `Locations`:`Hours per Week`) %>% 
  mutate(Dist.rounded = as.numeric(paste(Dist.rounded, 0, sep = ""))) %>% 
  pivot_longer(cols = c( `Locations`:`Hours per Week`)) %>% 
  mutate(`Treated Zips` = Counts_0 / 3) %>% 
  ggplot(aes(x = Dist.rounded, y = value)) + geom_point(aes(size = `Treated Zips`)) + facet_wrap(~name, scales = "free_y", ncol = 2) + xlim(0, 250) + 
  xlab("Kilometers to Competitive Zip") + ylab("Unadjusted Difference-in-differences") + theme_tufte_revised() + 
  geom_smooth(method = "lm", se = F, quiet = TRUE, formula = "y ~ x", mapping = aes(weight = `Treated Zips`)) + 
  geom_hline(yintercept=0, linetype = "dashed", color = "grey") + theme(text = element_text(size = 16)) + theme(title = element_text(face = "bold")) + 
  ggtitle("Figure 4 - Unadjusted DID Estimates by Distance to Competitive Zip")

@@

@@

## NumberofPatients and Total.Hours are the best cases, controlling for Sites
```{r}
df.spill3 <- df.spill2 %>% 
  left_join(census %>% select(ZipCode, YEAR, IncomeBelowPoverty, PovertyStatusDet), by = c("Year" = "YEAR", "Zip" = "ZipCode"))#%>% 
  # mutate(Poverty = IncomeBelowPoverty / PovertyStatusDet, 
  #        Unemployed = Unemployed / Unemp_denom, 
  #        Elderly = Age65andOver / TotalPop, 
  #        Black = Black / TotalPop, 
  #        Hispanic = Hispanic / TotalPop)

 i <- 10
  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)) ,
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- data.frame(model_feols_clustered$coeftable)[1,]
  TEs_Dist <- data.frame(model_feols_clustered$coeftable)[nrow(model_feols_clustered$coeftable),]

for (i in 12:19){
  df.temp <- df.spill3[,c(1:5, 11, i, 16:ncol(df.spill3))]
  names(df.temp)[1:7] <- c("Tx", "D", "Dist", "Year", "Zip", "Sites", 'Outcome')
  model_feols_clustered <- did2s(
      data = df.temp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Sites | Zip + Year , 
        second_stage = ~ i(Tx, ref = FALSE) + as.numeric(Dist / 10) + I(Tx *as.numeric(Dist / 10)),
        cluster_var = "Zip",
      verbose = FALSE
    )
  TEs <- rbind(TEs, data.frame(model_feols_clustered$coeftable)[1,])
  TEs_Dist <- rbind(TEs_Dist, data.frame(model_feols_clustered$coeftable)[3,])
}

did.access.figures <- df.spill3 %>% 
    mutate(Post = ifelse(Att.viz >= Year, 1, 0), 
         Treated = ifelse(Att > 0, 1, 0)) %>% 
  group_by(Post, Treated) %>% 
  select(Total.Hours, Perminance:Private) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Total.Hours:Private) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treated, Post), values_from = value) %>% 
  mutate(Unadjusted = (`1_1` - `1_0`) - (`0_1` - `0_0`)) %>% 
  cbind(Outcome = c("Hours Per Week","Perminance","Weekly Schedule","Calendar Schedule","Total","Uninsured","Medicaid","Medicare","Private")) %>% 
  select(Outcome, `0_0`, `0_1`, `1_0`, `1_1`, Unadjusted) %>% 
  cbind(TEs %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`)) %>% 
  cbind(TEs_Dist %>% mutate(Estimate = round(Estimate, 2), `95% CI` = paste(round(Estimate - 1.96 * `Std..Error`, 2), ", ", round(Estimate + 1.96 * `Std..Error`, 2), sep = "")) %>% select(Estimate, `95% CI`))

did.access.figures <- did.access.figures[c(5:9, 1, 3, 2, 4),]
rownames(did.access.figures) <- NULL

 did.access.figures %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","Estimate","95% CI")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  pack_rows(index = c("Patients" = 5, "Intensive Margin" = 2, "Extensive Margin" = 2)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "TE" = 2,"TE * Distance" = 2))
